\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome}
\usepackage{wasysym}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \small #4 \\ % Removed \textit from the second line
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Aditya Mokkapati} \\ \vspace{1pt}
    \small {+1(925)-895-3685} $|$ 
    \href{https://www.linkedin.com/in/aditya-mokkapati-am/}{\underline{linkedin.com/in/aditya-mokkapati-am}} $|$ 
    \href{mailto:amokkapa@gmail.com}{\underline{amokkapa@gmail.com}} $|$ 
    \href{https://github.com/amokkapati}{\underline{github.com/amokkapati}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{University of California, Santa Cruz}{September 2025 - June 2026}
{Computer Science M.S.}
{GPA: 4.0/4.0}

\resumeSubheading
{University of California, Santa Cruz}{September 2022 - June 2025}
{Computer Science B.S.}
{GPA: 3.9/4.0}

\vspace{5pt}
{\normalsize\textbf{Awards:} Dean’s Honors List (7x)} \\
{\normalsize\textbf{Relevant Coursework}: Intro to Data Structures and Analysis of Algorithms, Computer Architecture, Computer Systems Design, Applied Machine Learning, Artificial Intelligence, Networking Security}

\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
    \resumeSubHeadingListStart
          \resumeProjectHeading
              {\textbf{Workday, Software Engineer Intern}}{June 2025 - September 2025}
              \resumeItemListStart
     \resumeItem{Engineered synthetic traffic tests in Java, Playwright, and JUnit, simulating \textbf{1,000+} daily user sessions to enable real-time coverage and early testing.}

    \resumeItem{Reduced CI/CD pipeline build time by \textbf{80\%} \textbf{(30 → 5 min)} by integrating synthetic tests into Jenkins and optimized workflows with QA and Infra teams.} 

    \resumeItem{Deployed Grafana dashboards and PagerDuty alerts across \textbf{10+} environments, speeding up root-cause analysis and reducing MTTR by \textbf{2 hours} per incident.}

    \resumeItem{Prototyped LLM-based test-failure summarization using the OpenAI API; surfaced accuracy gaps that informed future automation plans.}
\resumeItemListEnd

    
    \resumeSubHeadingListEnd 
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Workday, Software Engineer Intern}}{June 2024 - September 2024}
          \resumeItemListStart
            \resumeItem{Built observability dashboards for the Public Cloud team, ingesting \textbf{10,000+} weekly events from \textbf{GitHub}, \textbf{Jira}, and \textbf{PagerDuty} to track DORA and sprint metrics.}

            \resumeItem{Enabled leadership to cut Jira delivery time by \textbf{30\%} and boost Terraform deployment frequency by \textbf{20\%} through metric-driven insights.}

            \resumeItem{Optimized Docker builds with multi-stage caching, shrinking environment build time \textbf{80\%} \textbf{(10 → 2 min)} and improving reproducibility across dev and cloud.}

            \resumeItem{Scaled AWS infrastructure (EC2, RDS, ALB, ASG) via Terraform to handle \textbf{3×} expected load with zero downtime during peak testing and dashboard use.}

          \resumeItemListEnd

\resumeSubHeadingListEnd 

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
\resumeProjectHeading
  {\textbf{NES-Style Console Emulator}}{}
  \resumeItemListStart
    \resumeItem{Built a C++ 8-bit emulator with separate CPU, memory, GPU, and controller modules; ran custom ROMs at 60 FPS with SDL2 rendering and 95\%+ instruction accuracy.}
    \resumeItem{Shipped cross-platform builds using CMake and FFmpeg, running on macOS, Windows, and Linux with input playback and MP4 debug export.}
    \resumeItem{Added input recording, replay, and save-state tools, cutting manual test time by 40\% and speeding up debugging.}
  \resumeItemListEnd
  
\resumeProjectHeading
    {{\textbf{Drought Severity Predictor}}}{}
    \resumeItemListStart
        \resumeItem{Built an experimental ML pipeline to classify drought severity levels (D0–D3) using historical climate data; explored hybrid models with PyTorch and XGBoost on structured tabular features.}
        \resumeItem{Implemented class rebalancing with SMOTETomek and hyperparameter tuning techniques (dropout, batch norm, learning rate scheduling); reached up to \textbf{82\%} accuracy in offline testing.}
        \resumeItem{Created a basic UI for scenario testing and feature importance visualization to inspect model decisions interactively.}
    \resumeItemListEnd
    \resumeSubHeadingListEnd
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item[] \small{
        \textbf{Languages:} Python, C, C++, Java, JavaScript\\
        \textbf{Developer Tools:} Docker, Jenkins, AWS(EC2, RDS, VPC), Terraform, Grafana, Git, Playwright, PyTorch, TensorFlow, React, Pandas, OpenAI API, JUnit, Unix\\
        \textbf{Certifications:} AWS Certified Cloud Practitioner \\

    }
\end{itemize}



%-------------------------------------------
\end{document}
